Some various methods for designing digital Finite Impulse Response (FIR) filters include frequency sampling methods, windowing-based methods, optimization based methods, and evolutionary optimization methods. Some of the reviewed literature about that are as follows:

\noindent
\begin{tabularx}{\columnwidth}{|M|M|M|M|M|}
	\hline
	\textbf{Ref. No.} & \textbf{Paper Title} & \textbf{Findings} & \textbf{Year}\\
	\hline
	\cite{article1} & A Review of Digital FIR Filter Design in Communication Systems & Various optimization techniques to design digital FIR filters. & 2021\\
	\hline
	\cite{202305.0334} & Comparative Analysis of RNN Versus IIR Digital Filtering to Optimize Resilience in pH Sensing & RNN-based digital filters have been shown to effectively suppress random pH perturbations. & 2023\\
	\hline
	\cite{rg1} & Comparison of Different Types of IIR Filters & The paper discusses the advantages of IIR filters over FIR filters. & 2016\\
	\hline
	\cite{rg2} & Comparison of the design of FIR and IIR filters for a given specification and removal of phase distortion from IIR filters &  This paper takes a given specification to design both FIR and IIR filter. An equalizer was also designed to remove the phase distortion of the IIR filter. & 2017\\
	\hline
	\cite{rg3} & Introduction to Sequence Learning Models: RNN, LSTM, GRU & Limitations of basic RNN and introduces LSTM, GRU \& BRNN.& 2021\\
	\hline
\end{tabularx}
\vspace{1\baselineskip}
\noindent
\begin{tabularx}{\columnwidth}{|M|M|M|M|M|}
	\hline
	\textbf{Ref. No.} & \textbf{Paper Title} & \textbf{Findings} & \textbf{Year}\\
	\hline
	\cite{en15207553} & Application of Deep Learning Gated Recurrent Unit in Hybrid Shunt Active Power Filter for Power Quality Enhancement & Unified filtering capability for power quality improvement in a three-phase, four-wire system. & 2022\\
	\hline
	\cite{sherstinsky2020fundamentals} & Fundamentals of recurrent neural network (RNN) and long short-term memory (LSTM) network & RNN framework of approximating an IIR system by an FIR model using LSTM. & 2020\\
	\hline
	\cite{app13031476} & A Hybrid CNN and RNN Variant Model for Music Classification & Music classification task by CNN and variants of RNN. & 2023\\
	\hline
	\cite{9258906} & A Dynamic Filtering DF-RNN Deep-Learning-Based Approach for EEG-Based Neurological Disorders Diagnosis & EEG-based diagnosis
	system well suited for two neurological disorders using GRU. & 2020\\
	\hline
	\cite{8618351} & HMFP-DBRNN: Real-Time Hand Motion Filtering and Prediction via Deep Bidirectional RNN & Parkinson's disease detection using DBRNN. & 2019\\
	\hline
\end{tabularx}
\vspace{1\baselineskip}
\noindent
\begin{tabularx}{\columnwidth}{|M|M|M|M|M|}
	\hline
	\textbf{Ref. No.} & \textbf{Paper Title} & \textbf{Findings} & \textbf{Year}\\
	\hline
	\cite{stefanova2004time} & Time Domain Recursive Digital Filter Modeling Based on Recurrent Neural Network Training & Modelling of time domain recursive digital filter using RNN. & 2004\\
	\hline
	\cite{595494} & A comparison between recurrent neural network architectures for digital equalization & This paper shows a comparison between three different first-order RNN architectures. & 1997\\
	\hline
	\cite{10.1007/978-90-481-9151-2_38} & One Approach for Training of Recurrent Neural Network Model of IIR Digital Filter &  & 2010\\
	\hline
	\cite{DBLP:journals/corr/abs-2005-09237} & Acoustic Echo Cancellation by Combining Adaptive Digital Filter and Recurrent Neural Network &  & 2020\\
	\hline
	\cite{6396136} & Digital IIR filters with minimal group delay for real-time applications &  & 2012\\
	\hline
	\cite{10.1007/978-90-481-3656-8_52} & One Dimensional IIR Digital Filter Modeling Based on Recurrent Neural Network &  & 2010\\
	\hline
\end{tabularx}
\vspace{1\baselineskip}

Some textbooks and online resources which provides the concept of Digital Signal Processing(DSP) and also discussed about the fundamentals of Analog and Digital filter design process. One of them provides the detailed concepts about Deep Learning, their applications, some standard deep learning models and the intuition behind them\cite{DigitalSignalProcessing}\cite{AnalogandDigitalFilterDesign}\cite{Goodfellow-et-al-2016}.