\begin{center}
	\LARGE \textbf{Acknowledgments}
	\vspace{1\baselineskip}
\end{center}

\textit{``I would like to express my sincere gratitude to my supervisors Dr. Priyank Singhal \& Mr. Vikas Kuchhal, my mentor Dr. Anu Sharma and jyotishacharya Mr. DK Lahori for providing me the guidance, valuable advice and constant encouragement that they provided during this seminar work. I am also greatly thankful to them as he has given me an opportunity to work on this interesting topic."}

\textit{``I am very grateful to Dr. RK Dwivedi the director of College of Computing Sciences \& Information Technology for providing me the opportunity to do this seminar as part of my academic program. This seminar has not only been a valuable learning experience but has also contributed to the knowledge base of the field."}

\textit{``I would also like to thank my seniors, colleagues and friends who provided me with valuable feedback and suggestions. Their inputs have significantly improved the quality of this seminar."}

\textit{``Furthermore, I would like to express my gratitude to Teerthanker Mahaveer University for providing me the necessary resources and infrastructure. The library staff and resources have all played an integral role in the successful completion of the study."}

\textit{``I am grateful to have had the opportunity to study at such an esteemed institution and to have been surrounded by individuals who have pushed me to achieve my best. Thank you, Teerthanker Mahaveer University, for contributing to my academic and personal growth."}

\textit{``Finally, I would like to thank my family for their unwavering support and encouragement throughout the research. Their love and understanding have been a source of strength and inspiration to me."}

\textit{``Once again, thank you to everyone who has contributed to this seminar."}

\vspace{2\baselineskip}

\begin{center}
	\begin{tabular}{p{0.67\linewidth}c}
		&  \textbf{\textit{-Mohit Singh}} \\
		&  CCSIT(TMU) \\
		& \today
	\end{tabular}
\end{center}
\clearpage