In the realm of digital signal processing, the pursuit of low-latency solutions remains paramount. This research introduces a pioneering approach — the ``Low Latency Digital Filter using Recurrent Neural Network." Leveraging the power of Recurrent Neural Networks (RNNs), this innovative filter seeks to overcome the limitations of traditional designs by providing swift adaptability to dynamic input signals. This brief overview highlights the motivation, design principles, and potential applications of this novel digital filter, aiming to contribute to the evolution of efficient real-time signal processing systems.

Digital Filters are the heart of DSP. From medical sector to entertainment industry, all the signal processing in the present digital world requires to deal with the discrete-time signals. Most of the time these signals requires filtering which is done by using a digital system known as the digital filter. On the other hand, RNNs in the field of Deep Learing are doing a great job. These type of neural networks are capable of predicting sequential data. This study is about presenting a new approach of designing a digital filter using RNN due to which one can achive a high quality output less latency.

Traditional filters, while effective, often face limitations in adapting swiftly to dynamic and rapidly changing input signals. The introduction of Recurrent Neural Networks, known for their ability to model temporal dependencies and handle sequential data, presents an intriguing avenue for advancing the field of digital filtering. This synopsis aims to present a comprehensive overview of the proposed ``Low Latency Digital Filter using Recurrent Neural Network," shedding light on its design principles, potential applications, and the anticipated advantages it offers in terms of reduced latency and improved adaptability.