Many machines are in our household items such as kitchen, bedroom, which are artificially intelligent to help us with our daily tasks, however, they are emotionally unintelligent to adapt to our fulfillment. If one desires an Artificial Intelligence, the Artificial Intelligence should be able to adapt to the individual's state of mind. At the present time, many leading companies have expanded the idea of Emotional Artificial Intelligence into their AI systems.\cite{ISSN-2456-2165}.

The need of EIM's are can be seen due to their numerous applications which are expanding rapidly.
Some of the common applications of EIM's include:
\begin{itemize}
	\item \textbf{Social Media:} They can be used in social media to analyse user's emotions and provide more personalized content.
	\item \textbf{Business Intelligence(BI) \& Operational Research(OR):} EIM's are more intelligent than the traditional machines as a result they can help in Decision Making which is involved in Business Intelligence \& Operational Research.
	\item \textbf{Human Resources:} In human resources to analyse employee's emotions and improve the work environment and productivity.
	\item \textbf{Development of Machine Ethics \& Computational Morality:} Emotional AI can play a vital role in the development of machine ethics and morality. It will allow machines to understand and respond to human emotions, which is an important component of ethical and moral decision-making.
	\item \textbf{Human-Computer Interaction(HCI):} Emotional AI is extremely helpful in HCI, as it enables computers to understand and respond to human emotions, making the interaction more natural, intuitive, and empathetic. Here are some ways in which Emotional AI can be useful in developing machine ethics and morality:
	\begin{itemize}
		\item \textbf{Understanding Human Emotions:} EAI can help machines to understand human emotions, which is an important component of ethical decision-making. For example, a machine that can detect when a human is experiencing fear or pain could adjust its behavior accordingly to avoid causing harm.
		\item \textbf{Ethical Decision-Making:} EAI can help machines to make more ethical decisions by taking into account human emotions and responses. For example, a self-driving car that can detect when a passenger is feeling anxious or stressed could adjust its driving style to provide a safer and more comfortable ride.
		\item \textbf{Morality and Empathy:} Emotional AI can help machines to exhibit more empathy towards humans, which is an important component of moral decision-making. For example, a robot that can detect when a human is feeling sad or lonely could provide comfort or companionship.
		\item \textbf{Human-Machine Collaboration:} Emotional AI can help facilitate collaboration between humans and machines by allowing machines to understand and respond to human emotions. This could lead to more effective and productive collaborations, as well as greater trust between humans and machines.
	\end{itemize}
	\item \textbf{Customer Service:} EAI can be used in customer service to understand customer's emotions and respond accordingly, improving customer satisfaction. It can also be used in getting customer reviews, feedbacks \& and conducting surveys.
	\item \textbf{Healthcare:} EAI could be very useful in healthcare sector to detect patient's emotions and provide appropriate treatment and care. They could be a great blessing for the treatment of psychic patients and for counselling of persons suffering form depression \& anxiety or even having suicidal tendency.
	\item \textbf{Education:} EAI can be used in education sector to improve the effectiveness of teaching by understanding the emotional state of the students and adapting the teaching method accordingly.
	\item \textbf{Marketing, Sales \& Advertisement:} EAI can be used in marketing to analyze customer's emotions and tailor marketing messages to maximize their impact which leads in increment of sales conversion rate.
	\item \textbf{Art \& Culture:} AI which can generate creative artistic content like Melodies \& Progressions in Music, Paintings \& Poetry is currently based on logical reasoning. By the development of Emotional AI, generation of this type of content can reach the next level of the arts which can also be used by the artists as a reference for their work.
	\item \textbf{Media \& Communication:} EAI has a huge potential to do great in the field of media as it can be used as a NEWS anchor or an interactive agent which can communicate with their listeners emoitionally.
	\item \textbf{Entertainment:} Emotionally Intelligent Machines can be used in the entertainment industry to create more immersive experiences for users by understanding their emotional responses, in gaming industry to create more engaging games that respond to the player's emotions also create the dynamic gaming environment accordingly, in movies industry to create ambience, environments and also in writing scripts.
\end{itemize}